Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-06-04 paper/ms.tex
Add better description of adiabatic experiment

{\bf Our method for initializing gas was arrived at after numerous attempts to
include enough gas in the simulation to be compatible with the Milky Way while
also not destroying the bar. For example, we tried evolving an exponential gas
disk adiabatically with the barred disk (i.e., no cooling, star formation, or
feedback). Because there is no mechanism to remove gas from the central region,
a large pileup of gas forms in the center.\footnote{{\bf We noticed that the bar
slows down in this adiabatic model which lacks a mechanism to remove gas from
the central region. \citet{2007ApJ...666..189B} also noted slowdown behavior in
models which lacked central gas removal. It appears that gas removal from the
center (in our model due to star formation) is necessary to stabilize a bar's
pattern speed.}} Once cooling is turned on, there is a sudden collapse of gas to
the center, destroying the bar. We don't believe our method is the only nor even
the best way to include gas. One advantage of our method, though, is that it
approximates the expectation that in the bar region the gas surface density
should be significantly reduced \citep[e.g.][]{1993RPPh...56..173S}}

>>>>

{\bf Our method for initializing gas was arrived at after numerous attempts to
include enough gas in the simulation to be compatible with the Milky Way while
also not destroying the bar. For example, we tried evolving an exponential gas
disk adiabatically with the barred disk (i.e., no cooling, star formation, or
feedback). Because there is no mechanism to remove gas from the central region,
a large, highly pressurized pileup of gas forms in the center.\footnote{{\bf We
noticed that the bar slows down in this adiabatic model which lacks a mechanism
to remove gas from the central region. \citet{2007ApJ...666..189B} also noted
slowdown behavior in models which lacked central gas removal. It appears that
gas removal from the center (in our model due to star formation) is necessary to
stabilize a bar's pattern speed.}} We then turned on the full SMUGGLE model. As
a result, there is a sudden collapse of gas to the center as pressure support is
lost due to cooling and star formation. This abrupt change in the potential
destroys the bar.

We don't believe our method is the only nor even the best way to include gas.
One advantage of our method, though, is that it approximates the expectation
that in the bar region the gas surface density should be significantly reduced
\citep[e.g.][]{1993RPPh...56..173S}}
